\cvsection{Work Experience} % SECTION TITLE
\begin{cventries} % CONTENT
  \cvsimpleentry
    {\textbf{VNG Corporation, Software Engineer - Backend}} % Job title
    {Vietnam, Mar. 2021 - Present} % Date
    {
      \begin{cvitems} % Description
        \item {Worked as a Game Backend Developer responsible for designing real-time communication protocols, implementing caching and data analytics systems, and maintaining stable game server infrastructure.}
        \item {Implemented a Java annotation-driven protocol generation system with inheritance support, reducing boilerplate code and improving communication scalability by 50\%. }
        \item {Used ClickHouse and Apache Superset to create real-time dashboards and achieved clear insights into player activity, revenue, and retention.}
        \item {Utilized Memcached for caching game state models and leaderboard data to enhance read efficiency and scalability.}
        \item {Integrated a Telegram chatbot to notify real-time triggers such as players achieving special milestones, improving game design insights and identifying critical bugs.}
        \item {Tech Stacks: Java, Kafka, ClickHouse, Apache Superset, Memcached, Docker.}
      \end{cvitems}
    }
  \cvsimpleentry
    {\textbf{VNG Corporation, Intern Software Engineer - Fullstack}} % Job title
    {Vietnam, Nov. 2020 - Feb. 2021} % Date
    {
      \begin{cvitems} % Description
        \item {As an intern, contributed to the end-to-end development of a game project, handling backend logic, frontend UI, and integrating them into a complete, deployable product}
      \end{cvitems}
    }


\end{cventries}
%docker run -u $UID:$GID --rm -v $PWD:/work csmith/awesome-cv-builder
