\cvsection{Projects} %	SECTION TITLE
\begin{cventries} %	CONTENT

  \cvsimpleentry
    {\href{https://github.com/anv99-vn/kafka-mini}{\textbf{Kafka-Mini}}} % Name
    {2026} % Date
    {
      \begin{cvitems} % Description
        \item {\textbf{GitHub}: \href{https://github.com/anv99-vn/kafka-mini}{https://github.com/anv99-vn/kafka-mini}}
        \item {Developed a lightweight, distributed message broker in \textbf{Go}, implementing core concepts such as topics, partitions, and consumer groups.}
        \item {Implemented the \textbf{Raft consensus algorithm} from scratch to ensure metadata consistency across broker nodes and enable automatic leader election.}
        \item {Designed a persistent storage engine using append-only log files (\textbf{.bin}) and indexes (\textbf{.idx}) to ensure high-performance message retrieval and durability.}
        \item {Engineered a \textbf{gRPC-based API} for client-broker communication, featuring \textbf{dynamic consumer group rebalancing} and offset management.}
      \end{cvitems}
    }

  \cvsimpleentry
    {\href{https://github.com/anv99-vn/db-java}{\textbf{DB-Java}}} % Name
    {2026} % Date
    {
      \begin{cvitems} % Description
        \item {\textbf{GitHub}: \href{https://github.com/anv99-vn/db-java}{https://github.com/anv99-vn/db-java}}
        \item {Developed a Relational Database Management System (RDBMS) in \textbf{Java}, featuring a custom SQL engine supporting CRUD operations and table management.}
        \item {Implemented a \textbf{disk-based B-Tree} indexing system to optimize query execution and manage large-scale data persistence effectively.}
        \item {Built a custom \textbf{SQL Tokenizer} and parser capable of processing complex queries with support for various data types and string literals.}
        \item {Engineered a block-based storage layer to manage physical data mapping on disk, ensuring data integrity and persistence across system restarts.}
      \end{cvitems}
    }

\end{cventries}
